% Awesome Source CV LaTeX Template
%
% This template has been downloaded from:
% https://github.com/darwiin/awesome-neue-latex-cv
%
% Author:
% Christophe Roger
%
% Template license:
% CC BY-SA 4.0 (https://creativecommons.org/licenses/by-sa/4.0/)

%Section: Project
\sectionTitle{Extracurricular activities}{\faLaptop}

\begin{projects}
	\project
	{TU/ecomotive}{2022 - 2023}
	{\website{https://www.tuecomotive.nl}{https://www.tuecomotive.nl}}
    {TU/ecomotive is a student team from the Eindhoven University of Technology that designs and builds concept cars around a sustainability theme. As Chief Electonics \& Software I helped design most of the electronic systems in the car. My main responsibilities were the drivetrain, communication network (CAN) and the lighting system.}
    {Embeddes Systems, CAN, PCB design, CAD, Teamwork, Leadership}

	\project
	{Advent of Code}{2022 - Present}
    {\github{LarsvanDartel/aoc-rust} \website{https://adventofcode.com}{https://adventofcode.com/}}
    {Advent of Code is an annual coding competition with daily challenges in December. I participate in the competition to improve my problem solving skills and learn new algorithms. For the last two years I won the competition within the Study association GEWIS.}
	{Rust, Python, Mathematica, Algorithms, Competitive programming}

	\project
	{Symbolic manipulation}{2023 - 2024}
    {\github{LarsvanDartel/symb-rs}}
    {As part of a team, I wrote a computer algebra system in Rust which uses recursive descent parsing to parse mathematical expressions. The system can simplify, differentiate and integrate expressions and show steps of the computaion.}
	{Rust, Mathematics, Computer Algebra}
\end{projects}
